Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-04-23 analyses/scripts/full_data_extraction_citation_table.Rmd
Revised the output settings to pdf

---
output:
  pdf_document:
    keep_tex: yes
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
# options(kableExtra.auto_format = FALSE,
#         knitr.table.format = "latex"
#         )

>>>>

---
output: 
  pdf_document:
    df_print: kable
    latex_engine: xelatex
    keep_tex: true
---
```{r setup, include=FALSE}
# options(kableExtra.auto_format = FALSE,
#         knitr.table.format = "latex"
#         )
